---
title: "Extra stuff"
output: html_document
date: "2022-11-23"
---


## Now let's try this as sample size grows

I put the results calculation from above into a function so we can try different sample sizes, etc. 

```{r}
source(here::here("scripts/sim_func.R"))
```

### Sample training,testing, validation at 300


```{r}
n_rep=100
results = sim_func(n_rep=n_rep,n_train=300,n_test=300,n_valid=300)
```

#### Coverage

```{r}
p1 = results %>% 
  arrange(beta_naive) %>%
  ggplot(aes(y = 1:n_rep))  + geom_point(aes(x=beta_naive,y=1:n_rep)) +
  geom_linerange(aes(xmin=low_naive, xmax=up_naive,col=cov_naive)) + 
  theme_minimal() + 
  geom_vline(xintercept=2) +
  xlim(-1,5)

p2 =  results %>% 
  arrange(beta_wang) %>%
  ggplot(aes(y = 1:n_rep)) + geom_point(aes(x=beta_wang,y=1:n_rep)) +
  geom_linerange(aes(xmin=low_wang, xmax=up_wang,col=cov_wang)) + 
  theme_minimal() + 
  geom_vline(xintercept=2) +
  xlim(-1,5)

p3 = results %>% 
  arrange(beta_oracle) %>%
  ggplot(aes(y = 1:n_rep)) + geom_point(aes(x=beta_oracle,y=1:n_rep)) +
  geom_linerange(aes(xmin=low_oracle, xmax=up_oracle,col=cov_oracle)) + 
  geom_vline(xintercept=2) +
  theme_minimal() + 
  xlim(-1,5)



p1 + p2 + p3
```

#### Standard errors

```{r}
results %>%
  select(se_naive,se_wang,se_oracle) %>%
  pivot_longer(1:3) %>%
  ggplot(aes(x=name,y=value)) +
  geom_boxplot() + 
  theme_minimal()

```

#### Estimates

```{r}
results %>%
  select(beta_naive,beta_wang,beta_oracle) %>%
  pivot_longer(1:3) %>%
  ggplot(aes(x=name,y=value)) +
  geom_boxplot() + 
  theme_minimal()

```



### Sample training,testing, validation at 100


```{r}
n_rep=100
results = sim_func(n_rep=n_rep,n_train=100,n_test=100,n_valid=100)
```

#### Coverage

```{r}
p1 = results %>% 
  arrange(beta_naive) %>%
  ggplot(aes(y = 1:n_rep))  + geom_point(aes(x=beta_naive,y=1:n_rep)) +
  geom_linerange(aes(xmin=low_naive, xmax=up_naive,col=cov_naive)) + 
  theme_minimal() + 
  geom_vline(xintercept=2) +
  xlim(-1,5)

p2 =  results %>% 
  arrange(beta_wang) %>%
  ggplot(aes(y = 1:n_rep)) + geom_point(aes(x=beta_wang,y=1:n_rep)) +
  geom_linerange(aes(xmin=low_wang, xmax=up_wang,col=cov_wang)) + 
  theme_minimal() + 
  geom_vline(xintercept=2) +
  xlim(-1,5)

p3 = results %>% 
  arrange(beta_oracle) %>%
  ggplot(aes(y = 1:n_rep)) + geom_point(aes(x=beta_oracle,y=1:n_rep)) +
  geom_linerange(aes(xmin=low_oracle, xmax=up_oracle,col=cov_oracle)) + 
  geom_vline(xintercept=2) +
  theme_minimal() + 
  xlim(-1,5)



p1 + p2 + p3
```

#### Standard errors

```{r}
results %>%
  select(se_naive,se_wang,se_oracle) %>%
  pivot_longer(1:3) %>%
  ggplot(aes(x=name,y=value)) +
  geom_boxplot() + 
  theme_minimal()

```

#### Estimates

```{r}
results %>%
  select(beta_naive,beta_wang,beta_oracle) %>%
  pivot_longer(1:3) %>%
  ggplot(aes(x=name,y=value)) +
  geom_boxplot() + 
  theme_minimal()

```



### Sample training,testing 100, validation 10,000


```{r}
n_rep=100
results = sim_func(n_rep=n_rep,n_train=100,n_test=100,n_valid=10000)
```

#### Coverage

```{r}
p1 = results %>% 
  arrange(beta_naive) %>%
  ggplot(aes(y = 1:n_rep))  + geom_point(aes(x=beta_naive,y=1:n_rep)) +
  geom_linerange(aes(xmin=low_naive, xmax=up_naive,col=cov_naive)) + 
  theme_minimal() + 
  geom_vline(xintercept=2) +
  xlim(-1,5)

p2 =  results %>% 
  arrange(beta_wang) %>%
  ggplot(aes(y = 1:n_rep)) + geom_point(aes(x=beta_wang,y=1:n_rep)) +
  geom_linerange(aes(xmin=low_wang, xmax=up_wang,col=cov_wang)) + 
  theme_minimal() + 
  geom_vline(xintercept=2) +
  xlim(-1,5)

p3 = results %>% 
  arrange(beta_oracle) %>%
  ggplot(aes(y = 1:n_rep)) + geom_point(aes(x=beta_oracle,y=1:n_rep)) +
  geom_linerange(aes(xmin=low_oracle, xmax=up_oracle,col=cov_oracle)) + 
  geom_vline(xintercept=2) +
  theme_minimal() + 
  xlim(-1,5)



p1 + p2 + p3
```

#### Standard errors

```{r}
results %>%
  select(se_naive,se_wang,se_oracle) %>%
  pivot_longer(1:3) %>%
  ggplot(aes(x=name,y=value)) +
  geom_boxplot() + 
  theme_minimal()

```

#### Estimates

```{r}
results %>%
  select(beta_naive,beta_wang,beta_oracle) %>%
  pivot_longer(1:3) %>%
  ggplot(aes(x=name,y=value)) +
  geom_boxplot() + 
  theme_minimal()

```



### Sample training,testing 1000, validation 100


```{r}
n_rep=100
results = sim_func(n_rep=n_rep,n_train=1000,n_test=1000,n_valid=100)
```

#### Coverage

```{r}
p1 = results %>% 
  arrange(beta_naive) %>%
  ggplot(aes(y = 1:n_rep))  + geom_point(aes(x=beta_naive,y=1:n_rep)) +
  geom_linerange(aes(xmin=low_naive, xmax=up_naive,col=cov_naive)) + 
  theme_minimal() + 
  geom_vline(xintercept=2) +
  xlim(-1,5)

p2 =  results %>% 
  arrange(beta_wang) %>%
  ggplot(aes(y = 1:n_rep)) + geom_point(aes(x=beta_wang,y=1:n_rep)) +
  geom_linerange(aes(xmin=low_wang, xmax=up_wang,col=cov_wang)) + 
  theme_minimal() + 
  geom_vline(xintercept=2) +
  xlim(-1,5)

p3 = results %>% 
  arrange(beta_oracle) %>%
  ggplot(aes(y = 1:n_rep)) + geom_point(aes(x=beta_oracle,y=1:n_rep)) +
  geom_linerange(aes(xmin=low_oracle, xmax=up_oracle,col=cov_oracle)) + 
  geom_vline(xintercept=2) +
  theme_minimal() + 
  xlim(-1,5)



p1 + p2 + p3
```

#### Standard errors

```{r}
results %>%
  select(se_naive,se_wang,se_oracle) %>%
  pivot_longer(1:3) %>%
  ggplot(aes(x=name,y=value)) +
  geom_boxplot() + 
  theme_minimal()

```

#### Estimates

```{r}
results %>%
  select(beta_naive,beta_wang,beta_oracle) %>%
  pivot_longer(1:3) %>%
  ggplot(aes(x=name,y=value)) +
  geom_boxplot() + 
  theme_minimal()

```

